Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-05-20 cover_letter/letterhead.tex
Cover letter updates

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
%\hspace*{\longindentation} % Move the signature right
%\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.0in
\includegraphics[width=0.2\textwidth]{signature_720}
%\vskip 0.65in % Whitespace between the signature text and your name
\\
\noindent
\fromsig
\vskip -0.05in
\titleone\\
\department\\
\institution\\
%\vskip -0.1in
%\noindent cc: M.S.~Jones, B.~Ashwood, A.~Tokmakoff
}

@@

Shoji Takada \hfill Biophysics, Graduate School of Science, Kyoto University \\
+81-(0)75-753-4070 \hfill \url{takada@ biophys.kyoto-u.ac.jp}

$\circ$ \textit{Expert in simulations of coarse-grained modeling of DNA-protein systems.}

Thomas Ouldridge \hfill  Bioengineering, Imperial College London \\
+44-(0)20-7589-5111 \hfill \url{t.ouldridge@implerial.ac.uk}

$\circ$ \textit{Expert in simulations of biochemical systems for nanotechnology applications.}

Modesto Orozco \hfill  Institute for Research in Biomedicine, University of Barcelona \\
+34-93-40-37156 \hfill \url{modesto.orozco@irbbarcelona.org}

$\circ$ \textit{Expert in molecular dynamics simulations of nucleic acids.}

>>>>

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
%\hspace*{\longindentation} % Move the signature right
%\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.0in
\includegraphics[width=0.2\textwidth]{signature_720}
%\vskip 0.65in % Whitespace between the signature text and your name
\\
\noindent
\fromsig
\vskip -0.05in
\titleone\\
\department\\
\institution\\
\vskip -0.1in
\noindent cc: M.S.~Jones, B.~Ashwood, A.~Tokmakoff
}

@@

%Shoji Takada \hfill Biophysics, Graduate School of Science, Kyoto University \\
%+81-(0)75-753-4070 \hfill \url{takada@ biophys.kyoto-u.ac.jp}

%$\circ$ \textit{Expert in simulations of coarse-grained modeling of DNA-protein systems.}

%Thomas Ouldridge \hfill  Bioengineering, Imperial College London \\
%+44-(0)20-7589-5111 \hfill \url{t.ouldridge@implerial.ac.uk}

%$\circ$ \textit{Expert in simulations of biochemical systems for nanotechnology applications.}

%Modesto Orozco \hfill  Institute for Research in Biomedicine, University of Barcelona \\
%+34-93-40-37156 \hfill \url{modesto.orozco@irbbarcelona.org}

%$\circ$ \textit{Expert in molecular dynamics simulations of nucleic acids.}
